Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-21 manuscript/manuscript.tex
Fixed mm in math text
Fixed typo on distance-size ratio

On the first iteration, the ratio $L_r/L_r^\text{orig} = 1$ because the tesseroid being
divided is the original one.
For future iterations, the ratio will be progressively smaller than one as the
tesseroids get smaller.
This is intended to limit the number of divisions to the ones that will
significantly reduce the numerical error:
dividing a large tesseroid with a small $\text{max}\{ \Delta \rho(r') \}$ would
improve the integration accuracy more than dividing a small tesseroid with a
higher $\text{max}\{ \Delta \rho(r') \}$.
We also do not divide tesseroids with $L_r < 1\ mm$ because any integration errors would
be negligible due to the small mass of the tesseroid..

@@

The distance-size ration $D$ of the adaptive discretization and the delta ratio $\delta$
of the density-based discretization determine how many times each tesseroid will be
divided and thus indirectly control the numerical error of the integration.
Optimal values for $D$ and $\delta$ must be determined in order to ensure both
acceptable numerical accuracy and computation efficiency for the algorithm.

>>>>

On the first iteration, the ratio $L_r/L_r^\text{orig} = 1$ because the tesseroid being
divided is the original one.
For future iterations, the ratio will be progressively smaller than one as the
tesseroids get smaller.
This is intended to limit the number of divisions to the ones that will
significantly reduce the numerical error:
dividing a large tesseroid with a small $\text{max}\{ \Delta \rho(r') \}$ would
improve the integration accuracy more than dividing a small tesseroid with a
higher $\text{max}\{ \Delta \rho(r') \}$.
We also do not divide tesseroids with $L_r < 1$ mm because any integration errors would
be negligible due to the small mass of the tesseroid..

@@

The distance-size ratio $D$ of the adaptive discretization and the delta ratio $\delta$
of the density-based discretization determine how many times each tesseroid will be
divided and thus indirectly control the numerical error of the integration.
Optimal values for $D$ and $\delta$ must be determined in order to ensure both
acceptable numerical accuracy and computation efficiency for the algorithm.
